Model LF

### 2022-11-16 max_dp endogen stød.Rmd
Commit

COMMENT> 
BEHAVIORAL> pconk_ds
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(pconk_ds) =  C_1+ C_2*TSLAG(LOG(pconk_ds),1) + C_3*TSLAG(LOG(yd1_hk_ds),1) + C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + C_5*TSLAG(LOG(fnw_hk),2) + C_6*TSDELTALOG(TSLAG(pconk_ds,2)) + C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + C_8*TSDELTALOG(yd1_hk_ds)  + C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk) + C_10*d_2008q4 + C_11*d_2018q2 + C_12*d_2020q1 + C_13* time
COEFF> C_1 C_2 C_3 C_4 C_5 C_6 C_7 C_8 C_9 C_10 C_11 C_12 C_13
STORE> coe(1)

@@

COMMENT> 
BEHAVIORAL> xk_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(xk_ds) =  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time
COEFF>  p_652 p_653 p_654 p_655 p_656 p_657 p_658 p_659 p_660
STORE> coe(8)

@@

  ##Sensitivites analyse
  prod_shock_sens = TIMESERIES(c(prod),   
                       START=c(2005,2),FREQ=4),

@@

#S_modelData$prod_ds_sens = prod_ds

@@

trade_balance_disc= (xk_ds_disc - mk_ds_disc)/yk_ds_disc
```

@@

trade_balance_disc_01= (xk_ds_disc_01 - mk_ds_disc_01)/yk_ds_disc_01

@@

plot(((ik_disc_01 - ik_disc)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

```{r}
plot(((yk_ds_disc_01 - yk_ds_disc) / yk_ds_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

>>>>

COMMENT> 
BEHAVIORAL> pconk_ds_used
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(pconk_ds_used) =  C_1+
C_2*TSLAG(LOG(pconk_ds),1) +
C_3*TSLAG(LOG(yd1_hk_ds),1) +
C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) +
C_5*TSLAG(LOG(fnw_hk),2) +
C_6*TSDELTALOG(TSLAG(pconk_ds,2)) +
C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + 
C_8*TSDELTALOG(yd1_hk_ds)  +
C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk)+ 
C_10*d_2008q4 +
C_11*d_2018q2 + 
C_12*d_2020q1 + 
C_13* time
COEFF> C_1 C_2 C_3 C_4 C_5 C_6 C_7 C_8 C_9 C_10 C_11 C_12 C_13
STORE> coe(1)

COMMENT> 
BEHAVIORAL> pconk_ds_disc
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(pconk_ds_disc) = 
CC_2*TSLAG(LOG(pconk_ds),1) +
CC_3*TSLAG(LOG(yd1_hk_ds),1) +
CC_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) +
CC_5*TSLAG(LOG(fnw_hk),2) +
CC_6*TSDELTALOG(TSLAG(pconk_ds,2)) +
CC_7*TSDELTALOG(TSLAG(pconk_ds,3)) + 
CC_8*TSDELTALOG(yd1_hk_ds)  +
CC_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk)+ 
CC_10*d_2008q4 +
CC_11*d_2018q2 + 
CC_12*d_2020q1 + 
CC_13* time
COEFF> CC_2 CC_3 CC_4 CC_5 CC_6 CC_7 CC_8 CC_9 CC_10 CC_11 CC_12 CC_13
STORE> coe(111)

COMMENT> 
IDENTITY> pconk_ds
EQ> pconk_ds= pconk_ds_used
if> disc <= 0
IDENTITY> pconk_ds
EQ> pconk_ds= pconk_ds_disc
if> disc > 0

@@

COMMENT> 
BEHAVIORAL> xk_ds_used
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(xk_ds_used) =  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time
COEFF>  p_652 p_653 p_654 p_655 p_656 p_657 p_658 p_659 p_660
STORE> coe(8)

COMMENT> 
BEHAVIORAL> xk_ds_disc
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(xk_ds_disc) =  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time
COEFF>  p_652 p_653 p_654 p_655 p_656 p_657 p_658 p_659 p_660
RESTRICT> p_656 = -0.1
STORE> coe(8)

COMMENT> 
IDENTITY> xk_ds
EQ> xk_ds= xk_ds_used
if> disc <= 0
IDENTITY> xk_ds
EQ> xk_ds= xk_ds_disc
if> disc > 0

@@

  ##Sensitivites analyse
  prod_shock_sens = TIMESERIES(c(prod),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_disc = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),
  pconk_ds_used = TIMESERIES(c(pconk_ds),   
                       START=c(2005,2),FREQ=4),

@@

#S_modelData$xk_ds_disc = xk_ds

@@

net_export_disc= (xk_ds_disc - mk_ds_disc)
```

@@

net_export_disc_01= (xk_ds_disc_01 - mk_ds_disc_01)

```{r}
par(mfrow=c(2,2))

@@

plot(((ik_disc_01 - ik_disc)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()

plot((yk_ds_disc_01 - yk_ds_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "GDP");
grid()

plot((net_export_disc_01 - net_export_disc), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Net-Export");
grid()
